Hemodynamic responses of the Parahippocampal Place Area to spatial cues in a movie and its audio-description

### 2020-10-19 paper/main.tex
adjust captions of figures

% summary if literature review
In summary, studies suggest that the PPA does preferably but not exclusively
respond to visually presented spatial information.
% shortcomings of previous studies: simplified stimuli
Nevertheless, all reviewed studies have in common that they employed a small set
of simplified stimuli to strictly control experimental conditions.
% shortcomings of previous studies: task-based paradigm
Further, they usually relied on explicit judgment-based tasks to ensure that
participants payed attention to the stimuli.
% disadvantage 1b: lack of validity
Paradigms using block designs accompanied with a task have the disadvantage that
they do not resemble our real-life experience and thus lack external validity
\citep{westfall2016fixing} as well as ecological validity
\citep{hasson2004intersubject}.
% disadvantage 2a: averaging for group results
Additionally, the reviewed studies averaged results across 7-11 subjects to
improve the signal-to-noise-ratio (SNR).
% disadvantage 2b: no individual level
The disadvantage here is that the averaging approach does not characterize brain
functions at an individual level, a prerequisite for the application of brain
imaging methods in individual diagnostics (cf. \cite{dubois2016building,
eickhoff2020towards}).
% open questions
This raises the question how the PPA behaves under life-like conditions, and how
group results a driven by individuals subjects especially in response to
audio-only stimulation\todo{``audio-only'' sounds meh?, MIH: Yes, and comes out of nowhere}.

% naturalistic stimuli
Paradigms using naturalistic stimuli like movies
\citep{hasson2008neurocinematics, sonkusare2019naturalistic} or narratives
\citep{honey2012not, lerner2011topographic, silbert2014coupled} offer complex,
continuous stimulation that better resemble the experience of our dynamic
environment.
% naturalistic stimuli review: intro
Two early studies using naturalistic stimuli suggest functional specialization
of brain areas is preserved during movie watching when many perceptual and
cognitive processes are triggered simultaneously \citep{bartels2004mapping,
hasson2004intersubject}.
% Bartels (2004): Film + GLM (but surprisingly did not annotate landscapes)
\cite{bartels2004mapping} manually annotated time points that depict faces and
human bodies in a 22 minute clip of the movie \textit{Tomorrow Never Dies}
\citep{tomorrowneverdies}.
% Bartels: results
Employing a general linear model (GLM) to model hemodynamic activity, these time
points correlated with increased activity in the ``fusiform face area''
\citep{kanwisher1997ffa} and ``extrastriate body area''
\citep{downing2001bodyarea} respectively.
% Hasson (2004): Film + (reverse) ISC
Employing a reverse intersubject correlation, \cite{hasson2004intersubject} used
a 30 minute clip of the movie \textit{The Good, the Bad, and the Ugly}
\citep{goodbadugly}.
% Hasson: method
fMRI brain volumes showing the highest hemodynamic activity in the PPA [across
(five) participants] were matched to the temporally corresponding movie frames.
% Hasson: results
Results revealed that corresponding movie frames depicted indoor and outdoor
scenes including buildings and open fields.
% summary naturalistic stimuli
Nevertheless, both studies used an audio-visual stimulus and again do not
address the question how the investigated functional areas respond during an
audio-only stimulus.

@@

% what we did: data source
In the current study, we analyze publicly available functional data
(studyforrest.org) of the same 14 participants watching a movie
\citep{hanke2016simultaneous} and listening to an audiobook.
\citep{hanke2014audiomovie}.
% PPA + movie + audio-description
We annotated cuts \todo{MIH: only cuts relevant?} in the movie ``Forrest Gump'' \citep{ForrestGumpMovie}, and
words spoken by an additional narrator in the movie's audio-description (i.e.
the movie's audio-only variant; \citep{ForrestGumpGermanAD}) to exploratorily
investigate how the parahippocampal gyrus behaves during more life-like
conditions free from any task.
% traditional GLM
We do this by analyzing our data by constructing GLM contrasts as canonically
used to analyze data from tightly controlled paradigms.
% focus on audio-description
Encouraged by \citep{aziz2008modulation}, we focus on the audio-description as
an audio-only paradigm. We further test the audio-description's localization
performance of a ``visual area'' in individual study participants by comparing
our results to results of a dedicated visual localizer experiment done with the
same participants \citep{sengupta2016extension}.
% results
Our results demonstrate that (a), (b), (c)... \todo{similar to abstract and
conclusion}

@@

\begin{figure*} \centering
    \includegraphics[width=\linewidth]{figures/group-slices}
    \caption{Mixed-effects group-level (N=14) GLM results. Significant clusters
        (Z>3.4, p<.05 cluster-corrected) are overlaid on the MNI152 T1-weighted
        head template (gray).
        Light gray: The audio-description's field-of-view
        (cf. \citep{hanke2014audiomovie}).
        Blue: the primary $t$-contrast for the audio-description comparing
        geometry-related nouns to non geometry-related nouns spoken by the
        audio-description's narrator (\texttt{geo, groom > all non-geo}).
        Red: the primary $t$-contrast for the movie comparing cuts to a new
        setting with cuts to a familiar perspective (\texttt{vse\_new >
        vpe\_old}).
        Black: outline of overlapping individual PPA ROIs      \citep{sengupta2016extension}.}
    \label{fig:group-slices}
\end{figure*}

@@

\begin{figure*} \centering
    \includegraphics[width=\linewidth]{figures/subs-thresh-ppa}
    \caption{Fixed-effects individual-level GLM results (Z>3.4, p<.05
    cluster-corrected). To facilitate comparisons across subjects, individual
    brains are aligned via non-linear transformation to a study-specific T2*
    group template that is co-registered to the MNI152 template with an affine
    transformation (12 degrees of freedom).
    Light gray: The
    audio-description's field-of-view (cf.  \citep{hanke2014audiomovie}).
    Black: outline of the subject-specific PPA ROIs.
    Blue:
    the primary $t$-contrast for the audio-description comparing
    geometry-related nouns to non-geometry-related nouns spoken by the
    audio-description's narrator (\texttt{geo, groom > all non-geo}).
    Red: the
    primary $t$-contrast for the movie comparing cuts to an unfamiliar setting
    with cuts within an familiar perspective (\texttt{vse\_new > vpe\_old}).
    } \label{fig:subs-thresh-ppa} \end{figure*}

@@

\begin{figure*} \centering
    \includegraphics[width=\linewidth]{figures/stability-slices}
    \caption{Stability of contrasts. Overlap of significant clusters (Z>3.4;
        p<.05, cluster corrected) of contrasts created to isolate the PPA.
        Contrasts provide decreasing congruency with the spatial layout
        hypothesis and/or progressively less data/events. The overlap across
        contrasts is overlaid on the MNI152 T1-weighted head template (gray).
        Light gray: The audio-description's field-of-view (cf.
        \citep{hanke2014audiomovie}). Blue: contrasts 1-8 for the
        audio-description (see Table \ref{tab:ao-contrasts}. Red: contrasts 1-5
        for the audio-visual movie (see Table \ref{tab:av-contrasts}. Black:
        outline of overlapping individual PPA ROIs
        \citep{sengupta2016extension}.} \label{fig:stability-slices}
    \end{figure*}

>>>>

% summary if literature review
In summary, studies suggest that the PPA does preferably but not exclusively
respond to visually presented spatial information.
% shortcomings of previous studies: simplified stimuli
Nevertheless, all reviewed studies have in common that they employed a small set
of simplified stimuli to strictly control experimental conditions.
% shortcomings of previous studies: task-based paradigm
Further, they usually relied on explicit judgment-based tasks to ensure that
participants payed attention to the stimuli.
% disadvantage 1b: lack of validity
Paradigms using block designs accompanied with a task have the disadvantage that
they do not resemble our real-life experience and thus lack external validity
\citep{westfall2016fixing} as well as ecological validity
\citep{hasson2004intersubject}.
% disadvantage 2a: averaging for group results
Additionally, the reviewed studies averaged results across 7-11 subjects to
improve the signal-to-noise-ratio (SNR).
% disadvantage 2b: no individual level
The disadvantage here is that the averaging approach does not characterize brain
functions at an individual level, a prerequisite for the application of brain
imaging methods in individual diagnostics (cf. \cite{dubois2016building,
eickhoff2020towards}).
% open questions
This raises the question how the PPA behaves under life-like conditions, and how
group results a driven by individuals subjects especially in response to
auditory stimulus\todo{this comes out of nowhere}.

% naturalistic stimuli
Paradigms using naturalistic stimuli like movies
\citep{hasson2008neurocinematics, sonkusare2019naturalistic} or narratives
\citep{honey2012not, lerner2011topographic, silbert2014coupled} offer complex,
continuous stimulation that better resemble the experience of our dynamic
environment.
% naturalistic stimuli review: intro
Two early studies using naturalistic stimuli suggest functional specialization
of brain areas is preserved during movie watching when many perceptual and
cognitive processes are triggered simultaneously \citep{bartels2004mapping,
hasson2004intersubject}.
% Bartels (2004): Film + GLM (but surprisingly did not annotate landscapes)
\cite{bartels2004mapping} manually annotated time points that depict faces and
human bodies in a 22 minute clip of the movie \textit{Tomorrow Never Dies}
\citep{tomorrowneverdies}.
% Bartels: results
Employing a general linear model (GLM) to model hemodynamic activity, these time
points correlated with increased activity in the ``fusiform face area''
\citep{kanwisher1997ffa} and ``extrastriate body area''
\citep{downing2001bodyarea} respectively.
% Hasson (2004): Film + (reverse) ISC
Employing a reverse intersubject correlation, \cite{hasson2004intersubject} used
a 30 minute clip of the movie \textit{The Good, the Bad, and the Ugly}
\citep{goodbadugly}.
% Hasson: method
fMRI brain volumes showing the highest hemodynamic activity in the PPA [across
(five) participants] were matched to the temporally corresponding movie frames.
% Hasson: results
Results revealed that corresponding movie frames depicted indoor and outdoor
scenes including buildings and open fields.
% summary naturalistic stimuli
Nevertheless, both studies used an audio-visual stimulus and again do not
address the question how the investigated functional areas respond during
auditory stimulation.

@@

% what we did: data source
In the current study, we analyze publicly available functional data
(studyforrest.org) of the same 14 participants watching a movie
\citep{hanke2016simultaneous} and listening to an audiobook.
\citep{hanke2014audiomovie}.
% PPA + movie + audio-description
We annotated cuts \todo{MIH: only cuts relevant?} in the movie ``Forrest Gump'' \citep{ForrestGumpMovie}, and
words spoken by an additional narrator in the movie's audio-description (i.e.
the movie's audio-only variant; \citep{ForrestGumpGermanAD}) to exploratorily
investigate how the parahippocampal gyrus behaves during more life-like
conditions free from any task.
% traditional GLM
We do this by analyzing our data by constructing GLM contrasts as canonically
used to analyze data from tightly controlled paradigms.
% focus on audio-description
Encouraged by \citep{aziz2008modulation}, we focus on the audio-description as
an exclusively auditory paradigm. We further test the audio-description's localization
performance of a ``visual area'' in individual study participants by comparing
our results to results of a dedicated visual localizer experiment done with the
same participants \citep{sengupta2016extension}.
% results
Our results demonstrate that (a), (b), (c)... \todo{similar to abstract and
conclusion}

@@

\begin{figure*} \centering
    \includegraphics[width=\linewidth]{figures/group-slices}
    \caption{Mixed-effects group-level (N=14) GLM results. Significant clusters
        (Z>3.4, p<.05 cluster-corrected) are overlaid on the MNI152 T1-weighted
        head template (gray).
        Light gray: The audio-description's field-of-view
        (cf. \citep{hanke2014audiomovie}).
        Black: outline of overlapping individual PPA ROIs.
        The results of audio-description's primary $t$-contrast (blue) that
        compares geometry-related nouns to non geometry-related nouns spoken by
        the audio-description's narrator (\texttt{geo, groom > all non-geo})
        are overlaid over the movie's primary $t$-contrast (blue) that compares
        cuts to a new setting with cuts to a familiar perspective
        (\texttt{vse\_new > vpe\_old}).
   \citep{sengupta2016extension}.}
    \label{fig:group-slices}
\end{figure*}

@@

\begin{figure*} \centering
    \includegraphics[width=\linewidth]{figures/subs-thresh-ppa}
    \caption{Fixed-effects individual-level GLM results (Z>3.4, p<.05
    cluster-corrected). To facilitate comparisons across subjects, individual
    brains are aligned via non-linear transformation to a study-specific T2*
    group template that is co-registered to the MNI152 template with an affine
    transformation (12 degrees of freedom).
    The results of audio-description's primary $t$-contrast (blue) that
    compares geometry-related nouns to non geometry-related nouns spoken by
    the audio-description's narrator (\texttt{geo, groom > all non-geo})
    are overlaid over the movie's primary $t$-contrast (blue) that compares
    cuts to new setting with cuts to a familiar perspective
    (\texttt{vse\_new > vpe\_old}).
    Black: outline of the subject-specific PPA ROIs.
    Light gray: The audio-description's field-of-view (cf.
    \citep{hanke2014audiomovie}).}
\label{fig:subs-thresh-ppa} \end{figure*}

@@

\begin{figure*} \centering
    \includegraphics[width=\linewidth]{figures/stability-slices}
    \caption{Stability of contrasts. Overlap of significant clusters (Z>3.4;
        p<.05, cluster corrected) of contrasts created to isolate the PPA.
        The audio-description's contrasts 1-8 (blue; \ref{tab:ao-contrasts})
        are overlaid over the audio-visual movie's contrasts 1-5 (red;
        \ref{tab:av-contrasts}), both on top of the MNI152 T1-weighted head
        template (gray).
        Black: outline of overlapping individual PPA ROIs.
        Light gray: The audio-description's field-of-view (cf.
        \citep{hanke2014audiomovie}).}
    \label{fig:stability-slices}
    \end{figure*}
